Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-06-07 Paper/paper.tex
Stop saying "best-fit"

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
    % mosaic.py 
  \end{center}
  \caption{Homogenised quasar luminosity functions at
    $\lambda=1450$\,\AA\ in redshift bins from $z=0.1$ to $6.5$.  The
    symbols show our inferred binned luminosity functions from various
    data sets:
    \citet[red]{2010AJ....139.2360S},
    \citet[green]{2009MNRAS.392...19C},
    \citet[dark blue]{2013ApJ...773...14R},
    \citet[light blue]{2011ApJ...728L..26G},
    \citet[yellow]{2016ApJ...829...33Y},
    \citet[DR7 brown]{2013ApJ...768..105M},
    \citet[Stripe 82 teal]{2013ApJ...768..105M},
    \citet[pink]{2016ApJ...833..222J},
    \citet[orange]{2010AJ....139..906W}, and
    \citet[grey]{2015ApJ...798...28K}.
    Open circles in corresponding colours indicate magnitude bins
    excluded due to incompleteness for the respective data sets.  The
    number of AGN before this selection is shown in parentheses; the
    selected number of AGN is shown outside parentheses.  In each
    redshift bin, the black curve shows the best-fit double power law
    model, which is represented by the median of the posterior
    probability distribution function.  The grey shaded area shows the
    one-sigma (68.26\%) uncertainty.  See Sections~\ref{sec:binnedlf}
    and \ref{sec:bins} for further details.}
  \label{fig:mosaic}
\end{figure*}

@@

%%GW: I would delete the z_bin column from the table. Otherwise the
%%reader might be confused what you are plotting in the figure. The
%%bin centers and the mean values are very similar anyway.--done (GK)
%%GW: Again 2.5<z<2.6 is missing--done (GK)
%%GW: I would add a column or a comment which redshift bins we
%%consider reliable. I'm afraid lazy people will just take the values
%%without thinking.
\begin{table*}
  % bins_tabulate.py; Nqso added by hand
  \caption{Best-fit double power law luminosity function parameters in
    various redshift bins.  The luminosity function parameters
    $\phi_*$, $M_*$, $\alpha$, and $\beta$ are defined in
    Equation~(\ref{eqn:dpl}), with $\beta$ denoting the faint-end
    slope.  Quasars in each bin have redshifts $z_\mathrm{min}\leq z <
    z_\mathrm{max}$.  The number of quasars in each bin is given by
    $N_\mathrm{qso}$.  The bin centre and sample mean redshift are
    given by $z_\mathrm{bin}$ and $\langle z\rangle$, respectively.
    Errors indicate one-sigma (68.26\%) uncertainties.  These values
    are shown in Figure~\ref{fig:evoln}.  The corresponding luminosity
    functions are shown in Figure~\ref{fig:mosaic}.  See
    Section~\ref{sec:bins} for further details.}
  \label{tab:bins}
  \begin{tabular}{cccr....}
    \hline
    $\langle z\rangle$ &
    $z_\mathrm{min}$ &
    $z_\mathrm{max}$ &
    $N_\mathrm{qso}$ &
    \multicolumn{1}{c}{$\log_{10}(\phi_*/$} &
    \multicolumn{1}{c}{$M_*$} &
    \multicolumn{1}{c}{$\alpha$} &
    \multicolumn{1}{c}{$\beta$} \\

@@

Our estimates for the double power law luminosity function are shown
in Figure~\ref{fig:mosaic} for 25 redshift bins.
%% JFH you are confusing terminology. posterior median and best-fit are not generally the same and you should
%% not refer to them as such. You are also not explaning what you mean by posterior median. Is this the
%% median of the individual marginalized posteriors? Or is it the median of the function that results from
%% the posterior distribution? Those are not generally the same, unless the model is linear in the parameters,
%% which it is not. Finally, best fit always means maximum likelihood, and that is certainly not what you are
%% plotting here, so don't say best-fit. You can say as our ``adopted model'' or ``fiducial model fit'' or
%% something like that. I would just explain waht you plot. 
The posterior median
is shown as the best-fit model at each redshift, while the grey shaded
region shows the one-sigma (68.26\%) uncertainty.  Consistent with
previous studies, the double power law model provides an excellent
description of the luminosity function model over almost the complete
range of redshifts spanned by the data.  It is only in the highest
redshift bin ($z=5.5$--$6.5$) that the data seem to favour a single
power law.  In this bin, the resultant posterior distribution of the
break magnitude $M_*$ is bimodal with favoured values at the faint
($M_*>-18$) and bright end of the data ($M_*<-30$).  While in the
literature the $z\sim 6$ AGN have been assumed to lie on the bright
end of the luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a
comparison with the luminosity function at lower redshifts ($z<5.5$)
suggests that these AGN should instead be understood to describe the
faint-end of a double power law.
%% JFH Okay so you need to be more clear here that what you mean is that the trend
%% from the plot is that M_star gets progressively brighter with redshift. This is not
%% obvious given what you write here. Indeed, it is not super obvious until one looks at FIgure 4, which
%% anyway has this prior already in it. 
Therefore, in light of the
low-redshift data, we use restricted priors in this
%% JFH Which redshift bin?? Make it more clear that this prior is put in to avoid bi-modal distributions
%% and it is informed by inspection of the lower redshift data. 
redshift bin: we
restrict the bright-end slope $\alpha$ to values less than $-4$,
%% JFH Something does not jive here, since the error bars you are showing on the high-z poitns cross
%% the -4 value of your prior? So either your prior is not a hard prior, or it is not exactly at -4
which
is equivalent to forcing $M_*$ to be at the bright end of the data.
Other parameters continue to have wide uniform priors.  This also
illustrates the importance of analysing the evolution of the QLF with
redshift.

@@

%% JFH I think you need to show at least one corner plot for your fits somewhere in the paper.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, yellow curves
    show the best-fit double power law luminosity function in that
    redshift bin.  Other curves show the three global evolution
    models.  Shaded regions show the one-sigma (68.26\%)
    uncertainties.}
  \label{fig:mosaic_global}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    models.  The symbols show the best-fit parameters with one-sigma
    (68.26\%) uncertainties in redshift bins from
    Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected by
    systematics and removed from the global analysis are shown in
    grey.  In each panel, the solid curves and shaded regions show the
    three best-fit global models with one-sigma uncertainties.
    Model~1 provides a better fit, but requires a rapid change in the
    faint-end slope at $z\sim 3.5$.}
  \label{fig:evoln_global}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    % rhoqso.py -- draw_withGlobal_multiple()
  \end{center}
  \caption{AGN number density evolution in the global model, when the
    luminosity function is integrated (from top to bottom) down to
    $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
    show the estimates from the best-fit double power law luminosity
    functions in various redshift bins, with vertical error bars
    denoting one-sigma (68.26\%) uncertainties.  Open circles show the
    same in redshifts bins affected by systematics.  Curves show the
    estimated density from the global models, with the accompanying
    shaded regions denoting the one-sigma uncertainty. }
  \label{fig:rhoqso}
\end{figure}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
      % gammapi.py -- draw_emissivity_18()
      % gammapi.py -- draw_emissivity_21()
    \end{tabular}
  \end{center}
  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
    fraction down to a limiting magnitude for a luminosity function
    integration limit of $M_{1450}=-18$ (left panel) and
    $M_{1450}=-21$ (right panel).  Black filled circles with error
    bars in both panels show the emissivity determinations in redshift
    bin deemed to have low systematic errors.  Open circles show
    emissivities for redshift bins that we remove from analysis due to
    high systematic errors.  Solid red curves in both panels show the
    best fit emissivity evolution model, with the shaded area showing
    the one-sigma (68.26\%) uncertainty.  Also shown for comparison in
    both panels are models by \citet[pentagon
      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
    \citet[square]{2015AA...578A..83G},
    \citet[triangle]{2018PASJ...70S..34A},
    \citet[circle]{2018AJ....155..131M},
    \citet[diamond]{2018MNRAS.474.2904P}, \citet[open
      rectangle]{2017ApJ...847L..15O}, \citet[dotted green
      curve]{2015ApJ...813L...8M}, \citet[dashed
      brown]{2012ApJ...746..125H}, \citet[dashed
      grey]{2017MNRAS.466.1160M}, \citet[dashed
      blue]{2013A&A...551A..29P}, \citet[solid
      cyan]{2016A&A...587A..41P}, \citet[solid
      blue]{2017A&A...608A..64C}, and \citet[brown]{2007A&A...472..443B}.}
  \label{fig:e912_2}
\end{figure*}

@@

Figure~\ref{fig:evoln_global} shows the parameter evolution in the
global models, by comparing it with the results from the fits in
individual redshift bins shown in Figure~\ref{fig:evoln}.  All three
models capture the steepening of the faint end of the luminosity
function towards higher redshifts.  The best-fit form of Model~1 is
shown by the black curves in Figure~\ref{fig:evoln_global}.  The
accompanying grey shaded area depicts the one-sigma (68.26\%)
uncertainty.  The model is in excellent agreement with the results of
the fits in redshift bins discussed in the previous section.
%% JFH Reference Figure 5 here as well.  
The
deviation of the BOSS quasars at $z=2$--$4$ from the smooth evolution
is again strikingly apparent.  So is
%% JFH , as is the deviation
the deviation of the SDSS and
2SLAQ quasars at $z<0.6$.  This is an indirect justification for the
data selection discussion previously in Section~\ref{sec:bins}.
Unfortunately, this model suffers
%% JFH suffers from 
with a remarkably sharp break in the
evolution of the faint-end slope $\beta$ at about $z\sim 3.5$.  As
seen in Figure~\ref{fig:evoln_global}, the data seem to require this
break, although it seems unlikely that such a sharp break at this
redshift would be physical.  Model 1 thus serves to emphasize the
necessity of better quality data at these redshifts.  Models 2 and 3
are shown in Figure~\ref{fig:evoln_global} by the green and orange
curves, respectively.  The corresponding best-fit parameter values are
tabulated in Table~\ref{tab:global}.

The evolution of the comoving number density of quasars is shown in
Figure~\ref{fig:rhoqso} when the luminosity function is integrated
down to different limits.  Similar to Figure~\ref{fig:evoln_global},
symbols show the best-fit values with one-sigma uncertainties from the
double power law fits to the data in redshift bins.
%% JFH I'm bothered by the fact that the symbols and error bars here arise from the parametric fits. In my opinion, you
%% should be able to plot the data on here with Poisson errors in exactly the same way that you do when you compute the binned
%% luminosity function data points? These symbols with errors should be the data to me, and not the result of your fitting procedure. 
Solid curves and
shaded regions show the global models.  This number density evolution
again highlights the systematic error in data at $z\sim 3$.  The
number density of AGN down to the limit of
%% JFH the deepest spectroscopic surveys 
spectroscopic data
($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$ at its peak.  This
density rapidly increases
%% JFH I think you mean decreases here
at low redshifts and then drops gradually at
high redshifts.  Figure~\ref{fig:rhoqso} also shows the familiar
downsizing feature in which the number density of faint AGN peaks at
lower redshifts than that of the bright AGN.  While the number density
of AGN with $M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN
with $M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at
which spectroscopic data exist, $M_*<-21$, the number density of qsos
peaks at $z\sim 1$.
%% JFH The figure is not consistent with this statement. The model showing M < 21 is peaking
%% just below z = 2. 
However, the difference between our three models
is dramatically evident in Figure~\ref{fig:rhoqso}.  Model~1 prefers a
decrease in the number density of faint quasars at $z\sim 3$ followed
by an increase at higher redshift.  This is caused by the rapid
steepening of the faint-end slope in this model at this redshift.
%% JFH Reference lower right panel of figure 6 here. 
Figure~\ref{fig:rhoqso} reveals another property of these models: when
extrapolated, the AGN number density diverges in all three models at
high redshifts.
%% JFH I think this is just an artifiact of your fitting procedure,
%% i.e. that these polynomial coefficients are unconstrained at really
%% high-z. Do these fits include the banados and MOrtlock quasars? In
%% that case the divergence should not occur, at least for the
%% brightest bin.  Furthermore, if you would make this plot with the
%% data instead of of integrating fits, you would be able to plot
%% those objects on here as well.
This is result of the steep faint-end slope at high
redshifts combined with the rapid brightening of the break luminosity.
While no data exist at redshift $z>7.5$, this divergent behaviour is
shared by previous models in the literature
\citep{2007ApJ...654..731H}.  Figure~\ref{fig:rhoqso} also shows that
although Models 2 and 3 exhibit regular behaviour in the evolution of
the AGN number density at $z\sim 3$, they do not fit the $z\sim
4$--$5$ data as well as Model 1.

\begin{table}
  \caption{Best-fit luminosity function evolution models.  These
    parameters are defined in Equations~(\ref{eqn:cbs}) and
    (\ref{eqn:beta}).  See Section~\ref{sec:global} for further
    details and the redshift range of validity of these models.
    Errors indicate one-sigma (68.26\%) uncertainties.  Model 2 is our
    preferred model.}
  \label{tab:global}
  \begin{tabular}{p{1.0cm}eee}
    \hline 
    Param. &
    \multicolumn{1}{c}{Model 1} &
    \multicolumn{1}{c}{Model 2} &
    \multicolumn{1}{c}{Model 3} \\
    \hline
    $c_{0,0}$ & -7.559^{+0.131}_{-0.139} & -7.084^{+0.136}_{-0.142} & -6.842^{+0.077}_{-0.076} \\     
    $c_{0,1}$ & 1.013^{+0.079}_{-0.072} & 0.753^{+0.080}_{-0.073} & 0.590^{+0.039}_{-0.041} \\        
    $c_{0,2}$ & -0.113^{+0.005}_{-0.005} & -0.096^{+0.004}_{-0.005} & -0.083^{+0.003}_{-0.003} \\
    \\
    $c_{1,0}$ & -17.006^{+0.230}_{-0.243} & -15.423^{+0.263}_{-0.261} & -15.140^{+0.144}_{-0.136} \\  
    $c_{1,1}$ & -5.548^{+0.156}_{-0.143} & -6.725^{+0.156}_{-0.171} & -6.910^{+0.091}_{-0.093} \\     
    $c_{1,2}$ & 0.588^{+0.016}_{-0.019} & 0.737^{+0.018}_{-0.015} & 0.750^{+0.012}_{-0.013} \\        
    $c_{1,3}$ & -0.023^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} \\
    \\
    $c_{2,0}$ & -3.246^{+0.121}_{-0.123} & -2.973^{+0.117}_{-0.133} & -2.950^{+0.105}_{-0.097} \\     
    $c_{2,1}$ & -0.250^{+0.048}_{-0.050} & -0.347^{+0.050}_{-0.050} & -0.363^{+0.040}_{-0.043} \\
    \\
    $c_{3,0}$ & -2.350^{+0.051}_{-0.060} & -2.545^{+0.123}_{-0.290} & -1.424^{+0.031}_{-0.031} \\     
    $c_{3,1}$ & 0.647^{+0.072}_{-0.060} & 1.581^{+0.520}_{-0.264} & -0.111^{+0.010}_{-0.010} \\       
    $c_{3,2}$ & 3.857^{+0.092}_{-0.073} & 2.102^{+0.450}_{-0.283} & \multicolumn{1}{c}{---} \\        
    $c_{3,3}$ & 27.534^{+41.364}_{-9.405} & 1.965^{+0.461}_{-0.464} & \multicolumn{1}{c}{---} \\      
    $c_{3,4}$ & -0.002^{+0.074}_{-0.082} & -0.641^{+0.169}_{-0.154} & \multicolumn{1}{c}{---} \\      
    \hline 
  \end{tabular}
\end{table}

@@

We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
especially for sharing their quasar selection functions.  It is a
pleasure to acknowledge useful discussions with James Aird, Eduardo
Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Martin Haehnelt, Paul
Hewett, David Hogg, Vikram Khaire, Sergey Koposov, Donald Lynden-Bell,
Roberto Maiolino, Richard McMahon, Daniel Mortlock, Ewald Puchwein,
Gordon Richards, Alberto Rorai, Bram Venemans and Stephen Warren.  GK
acknowledges support from ERC Advanced Grant 320596 `The Emergence of
Structure During the Epoch of Reionization'.
%% Joe, do you need to add anything to acknowledgements?

@@

>>>>

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
    % mosaic.py 
  \end{center}
  \caption{Homogenised quasar luminosity functions at
    $\lambda=1450$\,\AA\ in redshift bins from $z=0.1$ to $6.5$.  The
    symbols show our inferred binned luminosity functions from various
    data sets:
    \citet[red]{2010AJ....139.2360S},
    \citet[green]{2009MNRAS.392...19C},
    \citet[dark blue]{2013ApJ...773...14R},
    \citet[light blue]{2011ApJ...728L..26G},
    \citet[yellow]{2016ApJ...829...33Y},
    \citet[DR7 brown]{2013ApJ...768..105M},
    \citet[Stripe 82 teal]{2013ApJ...768..105M},
    \citet[pink]{2016ApJ...833..222J},
    \citet[orange]{2010AJ....139..906W}, and
    \citet[grey]{2015ApJ...798...28K}.
    Open circles in corresponding colours indicate magnitude bins
    excluded due to incompleteness for the respective data sets.  The
    number of AGN before this selection is shown in parentheses; the
    selected number of AGN is shown outside parentheses.  In each
    redshift bin, the black curve shows our fiducial double power law
    model fit, which is represented by the median of the posterior
    probability distribution function.  The grey shaded area shows the
    one-sigma (68.26\%) uncertainty.  See Sections~\ref{sec:binnedlf}
    and \ref{sec:bins} for further details.}
  \label{fig:mosaic}
\end{figure*}

@@

%%GW: I would delete the z_bin column from the table. Otherwise the
%%reader might be confused what you are plotting in the figure. The
%%bin centers and the mean values are very similar anyway.--done (GK)
%%GW: Again 2.5<z<2.6 is missing--done (GK)
%%GW: I would add a column or a comment which redshift bins we
%%consider reliable. I'm afraid lazy people will just take the values
%%without thinking.
\begin{table*}
  % bins_tabulate.py; Nqso added by hand
  \caption{Derived double power law luminosity function parameters in
    various redshift bins.  The luminosity function parameters
    $\phi_*$, $M_*$, $\alpha$, and $\beta$ are defined in
    Equation~(\ref{eqn:dpl}), with $\beta$ denoting the faint-end
    slope.  Quasars in each bin have redshifts $z_\mathrm{min}\leq z <
    z_\mathrm{max}$.  The number of quasars in each bin is given by
    $N_\mathrm{qso}$.  The bin centre and sample mean redshift are
    given by $z_\mathrm{bin}$ and $\langle z\rangle$, respectively.
    Errors indicate one-sigma (68.26\%) uncertainties.  These values
    are shown in Figure~\ref{fig:evoln}.  The corresponding luminosity
    functions are shown in Figure~\ref{fig:mosaic}.  See
    Section~\ref{sec:bins} for further details.}
  \label{tab:bins}
  \begin{tabular}{cccr....}
    \hline
    $\langle z\rangle$ &
    $z_\mathrm{min}$ &
    $z_\mathrm{max}$ &
    $N_\mathrm{qso}$ &
    \multicolumn{1}{c}{$\log_{10}(\phi_*/$} &
    \multicolumn{1}{c}{$M_*$} &
    \multicolumn{1}{c}{$\alpha$} &
    \multicolumn{1}{c}{$\beta$} \\

@@

Our estimates for the double power law luminosity function are shown
in Figure~\ref{fig:mosaic} for 25 redshift bins.
%% JFH you are confusing terminology. posterior median and best-fit are not generally the same and you should
%% not refer to them as such. You are also not explaning what you mean by posterior median. Is this the
%% median of the individual marginalized posteriors? Or is it the median of the function that results from
%% the posterior distribution? Those are not generally the same, unless the model is linear in the parameters,
%% which it is not. Finally, best fit always means maximum likelihood, and that is certainly not what you are
%% plotting here, so don't say best-fit. You can say as our ``adopted model'' or ``fiducial model fit'' or
%% something like that. I would just explain waht you plot. 
The posterior median is shown as our adopted model at each redshift,
while the grey shaded region shows the one-sigma (68.26\%)
uncertainty.  Consistent with previous studies, the double power law
model provides an excellent description of the luminosity function
model over almost the complete range of redshifts spanned by the data.
It is only in the highest redshift bin ($z=5.5$--$6.5$) that the data
seem to favour a single power law.  In this bin, the resultant
posterior distribution of the break magnitude $M_*$ is bimodal with
favoured values at the faint ($M_*>-18$) and bright end of the data
($M_*<-30$).  While in the literature the $z\sim 6$ AGN have been
assumed to lie on the bright end of the luminosity function
\citep[e.g.,][]{2016ApJ...833..222J}, a comparison with the luminosity
function at lower redshifts ($z<5.5$) suggests that these AGN should
instead be understood to describe the faint-end of a double power law.
%% JFH Okay so you need to be more clear here that what you mean is that the trend
%% from the plot is that M_star gets progressively brighter with redshift. This is not
%% obvious given what you write here. Indeed, it is not super obvious until one looks at FIgure 4, which
%% anyway has this prior already in it. 
Therefore, in light of the
low-redshift data, we use restricted priors in this
%% JFH Which redshift bin?? Make it more clear that this prior is put in to avoid bi-modal distributions
%% and it is informed by inspection of the lower redshift data. 
redshift bin: we
restrict the bright-end slope $\alpha$ to values less than $-4$,
%% JFH Something does not jive here, since the error bars you are showing on the high-z poitns cross
%% the -4 value of your prior? So either your prior is not a hard prior, or it is not exactly at -4
which
is equivalent to forcing $M_*$ to be at the bright end of the data.
Other parameters continue to have wide uniform priors.  This also
illustrates the importance of analysing the evolution of the QLF with
redshift.

@@

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, yellow curves
    show our fiducial double power law luminosity function model in
    that redshift bin.  Other curves show the three global evolution
    models.  Shaded regions show the one-sigma (68.26\%)
    uncertainties.}
  \label{fig:mosaic_global}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    models.  The symbols show the posterior median values of
    parameters with one-sigma (68.26\%) uncertainties in redshift bins
    from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
    by systematics and removed from the global analysis are shown in
    grey.  In each panel, the solid curves and shaded regions show the
    three derived global models with one-sigma uncertainties.  Model~1
    provides a better fit, but requires a rapid change in the
    faint-end slope at $z\sim 3.5$.}
  \label{fig:evoln_global}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    % rhoqso.py -- draw_withGlobal_multiple()
  \end{center}
  \caption{AGN number density evolution in the global model, when the
    luminosity function is integrated (from top to bottom) down to
    $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
    show the estimates from the our fiducual double power law
    luminosity function models in various redshift bins, with vertical
    error bars denoting one-sigma (68.26\%) uncertainties.  Open
    circles show the same in redshifts bins affected by systematics.
    Curves show the estimated density from the global models, with the
    accompanying shaded regions denoting the one-sigma uncertainty. }
  \label{fig:rhoqso}
\end{figure}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
      % gammapi.py -- draw_emissivity_18()
      % gammapi.py -- draw_emissivity_21()
    \end{tabular}
  \end{center}
  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
    fraction down to a limiting magnitude for a luminosity function
    integration limit of $M_{1450}=-18$ (left panel) and
    $M_{1450}=-21$ (right panel).  Black filled circles with error
    bars in both panels show the emissivity determinations in redshift
    bin deemed to have low systematic errors.  Open circles show
    emissivities for redshift bins that we remove from analysis due to
    high systematic errors.  Solid red curves in both panels show the
    derived posterior median emissivity evolution model, with the
    shaded area showing the one-sigma (68.26\%) uncertainty.  Also
    shown for comparison in both panels are models by \citet[pentagon
      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
    \citet[square]{2015AA...578A..83G},
    \citet[triangle]{2018PASJ...70S..34A},
    \citet[circle]{2018AJ....155..131M},
    \citet[diamond]{2018MNRAS.474.2904P}, \citet[open
      rectangle]{2017ApJ...847L..15O}, \citet[dotted green
      curve]{2015ApJ...813L...8M}, \citet[dashed
      brown]{2012ApJ...746..125H}, \citet[dashed
      grey]{2017MNRAS.466.1160M}, \citet[dashed
      blue]{2013A&A...551A..29P}, \citet[solid
      cyan]{2016A&A...587A..41P}, \citet[solid
      blue]{2017A&A...608A..64C}, and
    \citet[brown]{2007A&A...472..443B}.}
  \label{fig:e912_2}
\end{figure*}

@@

Figure~\ref{fig:evoln_global} shows the parameter evolution in the
global models, by comparing it with the results from the fits in
individual redshift bins shown in Figure~\ref{fig:evoln}.  All three
models capture the steepening of the faint end of the luminosity
function towards higher redshifts.  The adopted posterior median form
of Model~1 is shown by the black curves in
Figure~\ref{fig:evoln_global}.  The accompanying grey shaded area
depicts the one-sigma (68.26\%) uncertainty.  The model is in
excellent agreement with the results of the fits in redshift bins
discussed in the previous section.
%% JFH Reference Figure 5 here as well.  
The
deviation of the BOSS quasars at $z=2$--$4$ from the smooth evolution
is again strikingly apparent.  So is
%% JFH , as is the deviation
the deviation of the SDSS and
2SLAQ quasars at $z<0.6$.  This is an indirect justification for the
data selection discussion previously in Section~\ref{sec:bins}.
Unfortunately, this model suffers
%% JFH suffers from 
with a remarkably sharp break in the
evolution of the faint-end slope $\beta$ at about $z\sim 3.5$.  As
seen in Figure~\ref{fig:evoln_global}, the data seem to require this
break, although it seems unlikely that such a sharp break at this
redshift would be physical.  Model 1 thus serves to emphasize the
necessity of better quality data at these redshifts.  Models 2 and 3
are shown in Figure~\ref{fig:evoln_global} by the green and orange
curves, respectively.  The corresponding parameter values are
tabulated in Table~\ref{tab:global}.

The evolution of the comoving number density of quasars is shown in
Figure~\ref{fig:rhoqso} when the luminosity function is integrated
down to different limits.  Similar to Figure~\ref{fig:evoln_global},
symbols show the posterior median values with one-sigma uncertainties from the
double power law fits to the data in redshift bins.
%% JFH I'm bothered by the fact that the symbols and error bars here arise from the parametric fits. In my opinion, you
%% should be able to plot the data on here with Poisson errors in exactly the same way that you do when you compute the binned
%% luminosity function data points? These symbols with errors should be the data to me, and not the result of your fitting procedure. 
Solid curves and
shaded regions show the global models.  This number density evolution
again highlights the systematic error in data at $z\sim 3$.  The
number density of AGN down to the limit of
%% JFH the deepest spectroscopic surveys 
spectroscopic data
($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$ at its peak.  This
density rapidly increases
%% JFH I think you mean decreases here
at low redshifts and then drops gradually at
high redshifts.  Figure~\ref{fig:rhoqso} also shows the familiar
downsizing feature in which the number density of faint AGN peaks at
lower redshifts than that of the bright AGN.  While the number density
of AGN with $M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN
with $M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at
which spectroscopic data exist, $M_*<-21$, the number density of qsos
peaks at $z\sim 1$.
%% JFH The figure is not consistent with this statement. The model showing M < 21 is peaking
%% just below z = 2. 
However, the difference between our three models
is dramatically evident in Figure~\ref{fig:rhoqso}.  Model~1 prefers a
decrease in the number density of faint quasars at $z\sim 3$ followed
by an increase at higher redshift.  This is caused by the rapid
steepening of the faint-end slope in this model at this redshift.
%% JFH Reference lower right panel of figure 6 here. 
Figure~\ref{fig:rhoqso} reveals another property of these models: when
extrapolated, the AGN number density diverges in all three models at
high redshifts.
%% JFH I think this is just an artifiact of your fitting procedure,
%% i.e. that these polynomial coefficients are unconstrained at really
%% high-z. Do these fits include the banados and MOrtlock quasars? In
%% that case the divergence should not occur, at least for the
%% brightest bin.  Furthermore, if you would make this plot with the
%% data instead of of integrating fits, you would be able to plot
%% those objects on here as well.
This is result of the steep faint-end slope at high
redshifts combined with the rapid brightening of the break luminosity.
While no data exist at redshift $z>7.5$, this divergent behaviour is
shared by previous models in the literature
\citep{2007ApJ...654..731H}.  Figure~\ref{fig:rhoqso} also shows that
although Models 2 and 3 exhibit regular behaviour in the evolution of
the AGN number density at $z\sim 3$, they do not fit the $z\sim
4$--$5$ data as well as Model 1.

\begin{table}
  \caption{Derived luminosity function evolution models.  These
    parameters are defined in Equations~(\ref{eqn:cbs}) and
    (\ref{eqn:beta}).  See Section~\ref{sec:global} for further
    details and the redshift range of validity of these models.
    Errors indicate one-sigma (68.26\%) uncertainties.  Model 2 is our
    preferred model.}
  \label{tab:global}
  \begin{tabular}{p{1.0cm}eee}
    \hline 
    Param. &
    \multicolumn{1}{c}{Model 1} &
    \multicolumn{1}{c}{Model 2} &
    \multicolumn{1}{c}{Model 3} \\
    \hline
    $c_{0,0}$ & -7.559^{+0.131}_{-0.139} & -7.084^{+0.136}_{-0.142} & -6.842^{+0.077}_{-0.076} \\     
    $c_{0,1}$ & 1.013^{+0.079}_{-0.072} & 0.753^{+0.080}_{-0.073} & 0.590^{+0.039}_{-0.041} \\        
    $c_{0,2}$ & -0.113^{+0.005}_{-0.005} & -0.096^{+0.004}_{-0.005} & -0.083^{+0.003}_{-0.003} \\
    \\
    $c_{1,0}$ & -17.006^{+0.230}_{-0.243} & -15.423^{+0.263}_{-0.261} & -15.140^{+0.144}_{-0.136} \\  
    $c_{1,1}$ & -5.548^{+0.156}_{-0.143} & -6.725^{+0.156}_{-0.171} & -6.910^{+0.091}_{-0.093} \\     
    $c_{1,2}$ & 0.588^{+0.016}_{-0.019} & 0.737^{+0.018}_{-0.015} & 0.750^{+0.012}_{-0.013} \\        
    $c_{1,3}$ & -0.023^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} \\
    \\
    $c_{2,0}$ & -3.246^{+0.121}_{-0.123} & -2.973^{+0.117}_{-0.133} & -2.950^{+0.105}_{-0.097} \\     
    $c_{2,1}$ & -0.250^{+0.048}_{-0.050} & -0.347^{+0.050}_{-0.050} & -0.363^{+0.040}_{-0.043} \\
    \\
    $c_{3,0}$ & -2.350^{+0.051}_{-0.060} & -2.545^{+0.123}_{-0.290} & -1.424^{+0.031}_{-0.031} \\     
    $c_{3,1}$ & 0.647^{+0.072}_{-0.060} & 1.581^{+0.520}_{-0.264} & -0.111^{+0.010}_{-0.010} \\       
    $c_{3,2}$ & 3.857^{+0.092}_{-0.073} & 2.102^{+0.450}_{-0.283} & \multicolumn{1}{c}{---} \\        
    $c_{3,3}$ & 27.534^{+41.364}_{-9.405} & 1.965^{+0.461}_{-0.464} & \multicolumn{1}{c}{---} \\      
    $c_{3,4}$ & -0.002^{+0.074}_{-0.082} & -0.641^{+0.169}_{-0.154} & \multicolumn{1}{c}{---} \\      
    \hline 
  \end{tabular}
\end{table}

@@

We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
especially for sharing their quasar selection functions.  It is a
pleasure to acknowledge useful discussions with James Aird, Eduardo
Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov,
Donald Lynden-Bell, Roberto Maiolino, Richard McMahon, Daniel
Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
Venemans and Stephen Warren.  GK acknowledges support from ERC
Advanced Grant 320596 `The Emergence of Structure During the Epoch of
Reionization'.
%% Joe, do you need to add anything to acknowledgements?

@@

\section{Posterior distributions}
